---
title: "Exploratory Data Analysis, Sample Sizes, Figures, Summary Stats on Dispersal Distances in Gunung Palung National Park, Indonesia"
author: "Andrea Blackburn"
output: html_document

---

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(sm)
library(moments)
library(extrafont)
#library(remotes)
#remotes::install_version("Rttf2pt1", version = "1.3.8")
#extrafont::font_import()

dd<-read.csv("Bornean_orangutan_seed_dispersal_distances_dataset_12Dec22.csv")
dd$Age.sex<-as.factor(dd$Age.sex)
```

```{r}
library(lubridate)
dd$Date2<-dmy(dd$Date)
dd$mon<-month(dd$Date2)
dd$yr<-year(dd$Date2)
dd$mon_yr<-paste(dd$mon, dd$yr)

pheno<-read.csv("Pheno_2021.csv")
pheno$Date2<-dmy(pheno$Fake.Date)
pheno$mon<-month(pheno$Date2)
pheno$yr<-year(pheno$Date2)
pheno$mon_yr<-paste(pheno$mon,pheno$yr)

dd_to_export<-merge(dd, pheno, by="mon_yr")
write.csv(dd_to_export, "dd_to_export_12Dec22.csv")
```

###Graph of modeled dispersal distances by gut passage rates
```{r}
#create a dataset for each duration of gut passage 
#remove all NA's
dd45<-filter(dd, DD.45 != "0")
dd60<-filter(dd, DD.60 != "0")
dd80<-filter(dd, DD.80 != "0")
dd125<-filter(dd, DD.125 != "0")

w<-dd45$DD.45
x<-dd60$DD.60
y<-dd80$DD.80
z<-dd125$DD.125

#calculate skewness & kurtosis
#45-hour GRT
skewness(w)
kurtosis(w)
#60-hour GRT
skewness(x)
kurtosis(x)
#80-hour GRT
skewness(y)
kurtosis(y)
#125-hour GRT
skewness(z)
kurtosis(z)

#combine all dispersal distances into 1 vector
c_all<-c(w,y,x,z)
#add GRT 
names<-c(rep(45, length(w)), rep(60, length(x)), rep(80, length(y)), rep(125, length(z)))
#create a df
density<-data.frame(c_all, names)
density$names<-as.factor(density$names)

plot_disp_density_gut_passage_rate<- ggplot(density, aes(x=c_all, color = names)) + 
  geom_density(size=1.45) + 
  scale_color_manual(values=c("#4682B4", "#AF46B4", "#D6604D", "#4BB446"))+
  theme_classic() +
  #set numbers to scienctific format
  scale_y_continuous(labels=function(n){format(n, scientific = FALSE)})+
  xlab("Density") + ylab("Dispersal Distance (m)") +
  theme(legend.position = c(0.8, 0.8))+
  theme(axis.text.x = element_text(family = "Arial", size = 20)) +
  theme(axis.text.y = element_text(family = "Arial", size = 20)) +
  theme(axis.title.x = element_text(family = "Arial", size = 20)) +
  theme(axis.title.y = element_text(family = "Arial",vjust = 2,size = 20)) +
  theme(legend.title = element_text(family = "Arial", size = 19)) +
  theme(legend.text = element_text(family = "Arial", size = 18)) +
  guides(color = guide_legend(override.aes = list(fill = c("#4682B4", "#AF46B4", "#D6604D", "#4BB446")))) +
  labs(color ="Gut Passage\n   Times (hr)", size=15)
plot_disp_density_gut_passage_rate
  
ggsave("disp_density_gut_passage_rate_12dec22.png", plot=plot_disp_density_gut_passage_rate, dpi=350, width =10, height =7)
```
#### Mean, Variance, SD, & Maximum Dispersal Distances for each duration of gut transit time (45, 60, 80, 125-hours) and dispersal distances by age-sex class
Evidence of overdispersion  
Walimah (WA) and Bilbo (BIL) are in more than one age-sex class category  

```{r}
#sample sizes by age-sex class
table(dd$Age.sex)

#how many unique individuals per age-sex class
dd_null<-filter(dd, Age.sex == "Nulliparous Female") 
length(unique(dd_null$Orangutan))#8 orangutans

dd_par<-filter(dd, Age.sex == "Parous Female")
length(unique(dd_par$Orangutan))#13 orangutans

dd_flm<-filter(dd, Age.sex == "Flanged Male")
length(unique(dd_flm$Orangutan))#7 orangutans

dd_uflm<-filter(dd, Age.sex == "Unflanged Male")
length(unique(dd_uflm$Orangutan))#10 orangutans
```
Summary Stats (mean, standard deviation, and maximum) of seed dispersal distances for four gut retention times (GRT)
```{r}
summary_stats<- function(df, Distance, Age.sex) {
     print("sample size") 
     print(length(na.omit(Distance)))
     print("mean distance")
     print(mean(Distance, na.rm=TRUE))
     print("standard deviation")
     print(sd(Distance, na.rm=TRUE))
     print("mean distance by age-sex class")
     print(aggregate(Distance ~ Age.sex, data = df, FUN = mean, na.rm = TRUE))
     print("standard deviation by age-sex class")
     print(aggregate(Distance ~ Age.sex, data = df, FUN = sd, na.rm = TRUE))
     print("max distance by age-sex class")
     print(aggregate(Distance ~ Age.sex, data = df, FUN = max, na.rm = TRUE))
}

#45-hours-----
print("45-hours GRT")
summary_stats(dd45, dd45$DD.45, dd45$Age.sex)
#60-hours-----
print("60-hours GRT")
summary_stats(dd60, dd60$DD.60, dd60$Age.sex)
#80-hours-----
print("80-hours GRT")
summary_stats(dd80, dd80$DD.80, dd80$Age.sex)
#125-hours-----
print("125-hours GRT")
summary_stats(dd125, dd125$DD.125, dd125$Age.sex)

#only for lost & unable to follow series that lasted four or fewer days---------------------
#Filter for the lost follows for 45 and 60-hours GRT
dd45_lost<-filter(dd45, Lost_unable_to_follow == "Y")
dd60_lost<-filter(dd60, Lost_unable_to_follow == "Y")
#45-hours-----
print("45-hours GRT - Lost follow series")
summary_stats(dd45_lost, dd45_lost$DD.45, dd45_lost$Age.sex)
#60-hours-----
print("60-hours GRT - Lost follow series")
summary_stats(dd60_lost, dd60_lost$DD.60, dd60_lost$Age.sex)

#only for not lost follow series------------------------------------------
#Filter for the lost follows for 45 and 60-hours GRT
dd45_not_lost<-filter(dd45, Lost_unable_to_follow != "Y")
dd60_not_lost<-filter(dd60, Lost_unable_to_follow != "Y")

#45-hours-----
print("45-hours GRT - Not lost follow series")
summary_stats(dd45_not_lost, dd45_not_lost$DD.45, dd45_not_lost$Age.sex)
#60-hours-----
print("60-hours GRT - Not lost follow series")
summary_stats(dd60_not_lost, dd60_not_lost$DD.60, dd60_not_lost$Age.sex)
```
##Percent of dispersal distances >100m
```{r}
#45-hours
dd45_100<-filter(dd45, DD.45 >100)
97/113
#60-hours
dd60_100<-filter(dd60, DD.60 >100)
102/111
#80-hours
dd80_100<-filter(dd80, DD.80 >100)
85/89
#125-hours
dd125_100<-filter(dd125, DD.125 >100)
31/31
```

Seed dispersal distances by mature and ripe fruit availability (Z-scores) for all fruiting trees in pheno plots
```{r}
#--------45 hours

g1<-ggplot(dd45, aes(x=zscore_MR, y=DD.45))+
           geom_point(aes(colour=Age.sex, shape=Age.sex), size=3)+ theme_classic()+ 
           geom_smooth(method='lm', formula= y~x, colour="black", size=1, fill="Gainsboro")+
           xlab(" ") + ylab("Dispersal Distances (m)") +
           theme(axis.text.x = element_text(family = "Arial", size=16)) +
           theme(axis.text.y = element_text(family = "Arial", size=16)) +
           theme(axis.title.y = element_text(family = "Arial", vjust= 6, size = 20))+
           ggtitle("A") + 
           theme(plot.title = element_text(lineheight=.8, face="bold",family = "Arial", size=20))+
           theme(legend.title = element_blank())+theme(legend.position = "none")+
           scale_shape_manual(values=c(15, 16, 17, 18)) +
           scale_color_manual(values=c('#999999','#E69F00', '#56B4E9', 'black'))

g1

#--------60 hours
g2<-ggplot(dd60, aes(x=zscore_MR, y=DD.60))+
           geom_point(aes(colour=Age.sex, shape=Age.sex), size=3)+ theme_classic()+ 
           geom_smooth(method='lm', formula= y~x, colour="black", size=1, fill="Gainsboro")+
           xlab(" ") + ylab(" ") +
           theme(axis.text.x = element_text(family = "Arial", size=16)) +
           theme(axis.text.y = element_text(family = "Arial", size=16)) +
           ggtitle("B") + 
           theme(plot.title = element_text(lineheight=.8, face="bold",family = "Arial", size=20))+
           scale_shape_manual(values=c(15, 16, 17, 18)) +
           scale_color_manual(values=c('#999999','#E69F00', '#56B4E9', 'black'))+
           theme(legend.title = element_blank())+theme(legend.position = "none")
g2

#--------80 hours

g3<-ggplot(dd80, aes(x=zscore_MR, y=DD.80))+
          geom_point(aes(colour=Age.sex, shape=Age.sex), size=3)+ theme_classic()+ 
          geom_smooth(method='lm', formula= y~x, colour="black", size=1, fill="Gainsboro")+
           xlab("Fruit Availability (z-scores)") + ylab("Dispersal Distances (m)") +
           theme(axis.text.x = element_text(family = "Arial", size=16)) +
           theme(axis.text.y = element_text(family = "Arial", size=16)) +
           theme(axis.title.x = element_text(family = "Arial", vjust=-2, size=18)) +
           theme(axis.title.y = element_text(family = "Arial", vjust=6, size = 20))+
           ggtitle("C") + 
           theme(plot.title = element_text(lineheight=.8, face="bold",family = "Arial", size=20))+
           scale_shape_manual(values=c(15, 16, 17, 18))+
           scale_color_manual(values=c('#999999','#E69F00', '#56B4E9', 'black'))+
           theme(legend.title = element_blank())+theme(legend.position = "none")
g3

#--------125 hours
g4<-ggplot(dd125, aes(x=zscore_MR, y=DD.125))+
           geom_point(aes(colour=Age.sex, shape=Age.sex), size=3)+ theme_classic()+ 
           geom_smooth(method='lm', formula= y~x, colour="black", size=1, fill="Gainsboro")+
           xlab("Fruit Availability (z-scores)") +ylab(" ") +
           theme(axis.text.x = element_text(family = "Arial", size=16)) +
           theme(axis.text.y = element_text(family = "Arial", size=16)) +
           theme(axis.title.x = element_text(family = "Arial", vjust= -2, size=18)) +
           theme(legend.title = element_text(family = "Arial", size = 18)) +
           theme(legend.text = element_text(family = "Arial", size = 16))+
           labs(color='   Age-Sex Class', shape='   Age-Sex Class')+
           ggtitle("D") + 
           theme(plot.title = element_text(lineheight=.8, face="bold",family = "Arial", size=20))+
           scale_shape_manual(values=c(15, 16, 17, 18)) +
           scale_color_manual(values=c('#999999','#E69F00', '#56B4E9', 'black')) +  
           theme(legend.position = c(.65,2.1))
g4

#cowplot package
plot_of_grids<-plot_grid(g1, g2, g3, g4)
plot_of_grids

ggsave("Fruit available by dispersal distance 12Dec22.png", plot=plot_of_grids, dpi=350, width =14, height =10)

```
Function to make colors transparent (Thanks to A.J. Marshall)
```{r}
#set degree of transparency
my.alpha <- 80

makeTransparent <- function(black, alpha = my.alpha){
	newColor <- col2rgb(black)
	apply(newColor, 2, function(curcoldata)			
	     {rgb(red   = curcoldata[1],
	          green = curcoldata[2],
	          blue  = curcoldata[3],
	          alpha = alpha,
	          maxColorValue =  255)})
}
#select colors
cols<-c("#7D0541","#003399",  "#FF6633", "#614051")
tcols = makeTransparent(cols)
```
Boxplots of Dispersal distances by Gut retention time (hr)
```{r}
#SET WORKING DIRECTORY
setwd("C:/Users/black/Documents/Documents/Dissertation/Dispersal Distances Chapter/Manuscript/Modified Figures")
dd_rearranged_data<-read.csv("Dispersal_Distances_rearranged_12Dec22.csv")

dd_rearranged_data$GRT<-as.factor(dd_rearranged_data$GRT)
dd_rearranged_data$GRT <- factor(dd_rearranged_data$GRT, levels = c("45", "60", "80", "125"))

dd_grt_bp<-ggplot(data=dd_rearranged_data, aes(x=GRT, y=Distance, fill=Female.Age.sex.v2))+
  geom_boxplot() +theme_classic() +
  labs(y="Dispersal distances (m)", x="Gut retention time (hr)")+
  scale_fill_manual(values= tcols)+
  theme(axis.title = element_text(family  = "Arial", size=15)) + 
  theme(axis.text.x = element_text(family = "Arial", size=13)) +
  theme(axis.text.y = element_text(family = "Arial", size=13)) +
  labs(fill = "Age-Sex Class")+ 
  theme(legend.text = element_text(family = "Arial", size =12)) +
  theme(legend.title = element_text(family = "Arial", size=13, hjust = 0.5))+
  theme(legend.position = c(0.86, 0.86))
dd_grt_bp

#ggsave("disp_dist_all_23Jul.jpg", plot = dd_grt_bp, dpi = 600)

```

Boxplots of Dispersal distances by Gut retention time (hr) for lost vs not lost follow series
```{r}
#45 hours DD
glost45 <- ggplot(dd45, aes(x = Lost_unable_to_follow, y = DD.45)) +
  geom_boxplot() + theme_classic()

g_lost45 <- ggplot(dd45, aes(x = Lost_unable_to_follow, y = DD.45, fill = Age.sex)) +
  geom_boxplot() + theme_classic() +
  xlab("Follow Series Type")  + ylab("Dispersal distances (m)") +
  scale_x_discrete(labels = c("Not Lost", "Lost")) +
  ylim(0, 2300) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values=tcols)+
  theme(legend.position="top") +
  theme(legend.position = c(0.1, 0.9))+
  theme(axis.text.x = element_text(family = "Arial", size = 20)) +
  theme(axis.text.y = element_text(family = "Arial", size = 20)) +
  theme(axis.title.x = element_text(family = "Arial", size = 20, vjust =-0.2, 
               margin = margin(t = 20, r = 0, b = 0, l = 0))) +
  theme(axis.title.y = element_text(family = "Arial",vjust = 2,size = 20)) +
  theme(legend.title = element_text(family = "Arial", size = 18)) +
  theme(legend.text = element_text(family = "Arial", size = 17)) +
  labs(color ="Age Sex Class", fill ="Age Sex Class", size=17)+ 
  guides(size = guide_legend(nrow = 4, byrow = TRUE)) + ggtitle("A") +
  theme(plot.title = element_text(
    lineheight = .8,
    face = "bold",
    family = "Arial",
    size = 20
  ))

g_lost45

#ggsave("DD45 Follow Duration.png", plot=g5_s, dpi=350, width =9, height =7)
#ggsave("Dispersal by Follow Duration and Age-Sex Class 45-hours 12Dec22.png", plot=g_lost45, dpi=350, width =9, height =7)


#60 hours DD
g8<-ggplot(dd60, aes(x=Lost_unable_to_follow, y=DD.60))+
  geom_boxplot()+ theme_classic()
g8

g_lost60 <- ggplot(dd60, aes(x = Lost_unable_to_follow, y = DD.60, fill = Age.sex)) +
  geom_boxplot(show.legend = FALSE) + theme_classic() +
  xlab("Follow Series Type") + ylab("") +
  scale_x_discrete(labels = c("Not Lost", "Lost")) +
  scale_color_manual(values =cols) +
  scale_fill_manual(values= tcols)+
  ylim(0, 2300) +
    theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(axis.text.x = element_text(family = "Arial", size = 20)) +
  theme(axis.title.x = element_text(family = "Arial", size = 20, vjust =-0.2, 
               margin = margin(t = 20, r = 0, b = 0, l = 0))) +
  theme(legend.title = element_blank())+
  theme(legend.text = element_blank())+
  labs(color ="Age Sex Class", fill ="Age Sex Class", size=17)+ 
  guides(size = guide_legend(nrow = 4, byrow = TRUE)) + ggtitle("B") +
  theme(plot.title = element_text(
    lineheight = .8,
    face = "bold",
    family = "Arial",
    size = 20
  ))

g_lost60 
#ggsave("Dispersal by Follow Duration and Age-Sex Class 60-hours 12Dec22.png", plot=g_lost60 , dpi=350, width =9, height =7)

#Plot both graphs:
g_both<-plot_grid(g_lost45 , g_lost60 , nrow=1)
g_both
#ggsave("Dispersal by Follow Duration and Age-Sex Class 12Dec22.png", plot=g_both, dpi=350, width =15, height =8)
```
