---
title: "Modeling Bornean Orangutan Seed Dispersal Across Habitats in Gunung Palung National Park, Indonesia"
author: "Andrea Blackburn"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(lubridate)
library(sm)
library(MASS)
library(lme4)
library(effects)
library(DHARMa)
library(bbmle)
library(stringr)
library(gridExtra)
library(extrafont)

#font_import()
#loadfonts(device = "win")
#windowsFonts()
```

```{r}
#read in seed dispersal distances dataset
#dataset contains phenology data (column zscore_MR)
dd<-read.csv("Bornean_orangutan_seed_dispersal_distances_dataset.csv")
dd<-tbl_df(dd)

#remove all NA's 
dd1<-filter(dd_buah, DD.45 != "0")
dd2<-filter(dd_buah, DD.60 != "0")
dd3<-filter(dd_buah, DD.80 != "0")
dd4<-filter(dd_buah, DD.125 != "0")
```

##Habitat Matching---------------------------------------------------------------------------- 
Does the at habitat 45, 60, 80, 125 hours match the initial feeding habitat?  

```{r}
library(plyr)
dd1$match45<-(dd1$Hab_Feed==dd1$Hab_T45)
m45<-count((dd1$match45==TRUE))
(m45[1,2]/(length(dd1$match45)))*100
#35% do NOT match
#Counted 45 hours in .csv

dd2$match60<-dd2$Hab_Feed==dd2$Hab_T60
m60<-count(dd2$match60==TRUE)
(m60[1,2]/(length(dd2$match60)))*100
#46% do NOT match

dd3$match80<-dd3$Hab_Feed==dd3$Hab_T80
m80<-count(dd3$match80==TRUE)
(m80[1,2]/(length(dd3$match80)))*100
#47.2% do NOT match

dd4$match125<-dd4$Hab_Feed==dd4$Hab_T125
m125<-count(dd4$match125==TRUE)
(m125[1,2]/(length(dd4$match125)))*100
#41.9% do NOT match

detach(package:plyr)
``` 
#----------------plotting seed dispersal across habitat types
###45 hour dispersal distances
Rearranging data for plot
```{r}
#paste to combine habitat types into one column
dd1$habitat_pairs<-paste(dd1$Hab_Feed, dd1$Hab_T45 , sep = " ")

#group_by: count the number of each habitat pairs
dd1_habs<-dd1%>%
  group_by(habitat_pairs) %>%
  summarize(hab_pairs= length(habitat_pairs))%>%
  ungroup()

dd1_plot<-merge(dd1, dd1_habs, by = "habitat_pairs")

habs<-c(dd1_plot$Hab_Feed, dd1_plot$Hab_T45)
hab_labels<-c(rep("feed", length(dd1_plot$Hab_Feed)), rep("hab45", length(dd1_plot$Hab_T45)))
habitat_pairs<-c(dd1_plot$habitat_pairs, dd1_plot$habitat_pairs)
hab_pairs<-c(dd1_plot$hab_pairs, dd1_plot$hab_pairs)

dd1_plot2<-data.frame(habs, hab_labels, habitat_pairs, hab_pairs)
dd1_plot2$hab_pairs<-as.factor(dd1_plot2$hab_pairs)

dd1_plot2<-filter(dd1_plot2, habitat_pairs != "Alluvial Alluvial")
dd1_plot2<-filter(dd1_plot2, habitat_pairs != "Peat Peat")
dd1_plot2<-filter(dd1_plot2, habitat_pairs != "Lowland Lowland" )
dd1_plot2<-filter(dd1_plot2, habitat_pairs != "Freshwater Freshwater")
#dd1_plot2<-filter(dd1_plot2, habitat_pairs != "Granite Lowland Granite Lowland")   

dd1_plot2$habs<-as.factor(dd1_plot2$habs)
levels(dd1_plot2$habs)
dd1_plot2$habs <- ordered(dd1_plot2$habs, levels = c("Peat", "Freshwater", "Alluvial", "Lowland"))
dd1_plot2$habs <- factor(dd1_plot2$habs, levels=rev(levels(dd1_plot2$habs)))
dd1_plot2$habs

```
#60 hours dispersal distances
Rearranging data for plot
```{r}
#paste to combine habitat types into one column
dd2$habitat_pairs<-paste(dd2$Hab_Feed, dd2$Hab_T60 , sep = " ")

#group_by: count the number of each habitat pairs
dd2_habs<-dd2%>%
  group_by(habitat_pairs) %>%
  summarize(hab_pairs= length(habitat_pairs))%>%
  ungroup()

dd2_plot<-merge(dd2, dd2_habs, by = "habitat_pairs")

habs<-c(dd2_plot$Hab_Feed, dd2_plot$Hab_T60)
hab_labels<-c(rep("feed", length(dd2_plot$Hab_Feed)), rep("hab60", length(dd2_plot$Hab_T60)))
habitat_pairs<-c(dd2_plot$habitat_pairs, dd2_plot$habitat_pairs)
hab_pairs<-c(dd2_plot$hab_pairs, dd2_plot$hab_pairs)

dd2_plot2<-data.frame(habs, hab_labels, habitat_pairs, hab_pairs)
dd2_plot2$hab_pairs<-as.factor(dd2_plot2$hab_pairs)

dd2_plot2<-filter(dd2_plot2, habitat_pairs != "Alluvial Alluvial")
dd2_plot2<-filter(dd2_plot2, habitat_pairs != "Peat Peat")
dd2_plot2<-filter(dd2_plot2, habitat_pairs != "Lowland Lowland" )
dd2_plot2<-filter(dd2_plot2, habitat_pairs != "Freshwater Freshwater")
#dd2_plot2<-filter(dd2_plot2, habitat_pairs != "Granite Lowland Granite Lowland")   

dd2_plot2$habs<-as.factor(dd2_plot2$habs)
levels(dd2_plot2$habs)
dd2_plot2$habs <- ordered(dd2_plot2$habs, levels = c("Peat", "Freshwater", "Alluvial", "Lowland"))
dd2_plot2$habs <- factor(dd2_plot2$habs, levels=rev(levels(dd2_plot2$habs)))
dd2_plot2$habs
            
```
#80 hours dispersal distances 
Rearranging data for plot
```{r}
#paste to combine habitat types into one column
dd3$habitat_pairs<-paste(dd3$Hab_Feed, dd3$Hab_T80 , sep = " ")

#group_by: count the numbe rof each habitat pairs
dd3_habs<-dd3%>%
  group_by(habitat_pairs) %>%
  summarize(hab_pairs= length(habitat_pairs))%>%
  ungroup()

dd3_plot<-merge(dd3, dd3_habs, by = "habitat_pairs")

habs<-c(dd3_plot$Hab_Feed, dd3_plot$Hab_T80)
hab_labels<-c(rep("feed", length(dd3_plot$Hab_Feed)), rep("hab80", length(dd3_plot$Hab_T80)))
habitat_pairs<-c(dd3_plot$habitat_pairs, dd3_plot$habitat_pairs)
hab_pairs<-c(dd3_plot$hab_pairs, dd3_plot$hab_pairs)

dd3_plot2<-data.frame(habs, hab_labels, habitat_pairs, hab_pairs)
dd3_plot2$hab_pairs<-as.factor(dd3_plot2$hab_pairs)

dd3_plot2<-filter(dd3_plot2, habitat_pairs != "Alluvial Alluvial")
dd3_plot2<-filter(dd3_plot2, habitat_pairs != "Peat Peat")
dd3_plot2<-filter(dd3_plot2, habitat_pairs != "Lowland Lowland" )
dd3_plot2<-filter(dd3_plot2, habitat_pairs != "Freshwater Freshwater")
#dd3_plot2<-filter(dd3_plot2, habitat_pairs != "Granite Lowland Granite Lowland")

dd3_plot2$habs<-as.factor(dd3_plot2$habs)
levels(dd3_plot2$habs)
dd3_plot2$habs <- ordered(dd3_plot2$habs, levels = c("Peat", "Freshwater", "Alluvial", "Lowland"))
dd3_plot2$habs <- factor(dd3_plot2$habs, levels=rev(levels(dd3_plot2$habs)))
dd3_plot2$habs

```
#125 Hours Dispersal Distances
Rearranging data for plot
```{r}
#paste to combine habitat types into one column
dd4$habitat_pairs<-paste(dd4$Hab_Feed, dd4$Hab_T125 , sep = " ")

#group_by: count the number of each habitat pairs
dd4_habs<-dd4%>%
  group_by(habitat_pairs) %>%
  summarize(hab_pairs= length(habitat_pairs))%>%
  ungroup()

dd4_plot<-merge(dd4, dd4_habs, by = "habitat_pairs")

habs<-c(dd4_plot$Hab_Feed, dd4_plot$Hab_T125)
hab_labels<-c(rep("feed", length(dd4_plot$Hab_Feed)), rep("hab125", length(dd4_plot$Hab_T125)))
habitat_pairs<-c(dd4_plot$habitat_pairs, dd4_plot$habitat_pairs)
hab_pairs<-c(dd4_plot$hab_pairs, dd4_plot$hab_pairs)

dd4_plot2<-data.frame(habs, hab_labels, habitat_pairs, hab_pairs)
dd4_plot2$hab_pairs<-as.factor(dd4_plot2$hab_pairs)

dd4_plot2<-filter(dd4_plot2, habitat_pairs != "Alluvial Alluvial")
dd4_plot2<-filter(dd4_plot2, habitat_pairs != "Peat Peat")
dd4_plot2<-filter(dd4_plot2, habitat_pairs != "Lowland Lowland" )
dd4_plot2<-filter(dd4_plot2, habitat_pairs != "Freshwater Freshwater")
#dd4_plot2<-filter(dd4_plot2, habitat_pairs != "Granite Lowland Granite Lowland")

dd4_plot2$habs<-as.factor(dd4_plot2$habs)
levels(dd4_plot2$habs)
dd4_plot2$habs <- ordered(dd4_plot2$habs, levels = c("Peat", "Freshwater", "Alluvial", "Lowland"))
dd4_plot2$habs <- factor(dd4_plot2$habs, levels=rev(levels(dd4_plot2$habs)))
dd4_plot2$habs
levels(dd4_plot2$habs)
```
###function to make colors transparent (Thanks to A.J. Marshall)
```{r}
#all
cols<-c("#566D7E", "#307D7E", "#B38481", "#7E354D", "#D4A017", "#C35817", "#C34A2C", "#800517", "#7D0541", "#614051")
#cols<-c("Marble Blue","Greenish Blue", "Rosy Brown", "Velvet Maroon", "Orange Gold", "Red Fox", "Chestnut Red", "Firebrick", "Plum Pie", "Eggplant")

my.alpha <- 100

makeTransparent <- function(black, alpha = my.alpha){
	newColor <- col2rgb(black)
	apply(newColor, 2, function(curcoldata)			
	     {rgb(red   = curcoldata[1],
	          green = curcoldata[2],
	          blue  = curcoldata[3],
	          alpha = alpha,
	          maxColorValue =  255)})
}
tcols = makeTransparent(cols)
```

Graphing modeled orangutan seed dispersal across habitat types in Gunung Palung National Park

```{r}
plot1<-ggplot(dd1_plot2, aes(x=hab_labels, y = habs, group= habitat_pairs, size=hab_pairs, color=hab_pairs)) + theme_bw()+
    geom_line() +
    scale_size_manual(values = c(1,2,3,4,5,6,7,8), labels=c("1", "2", "3", "4", "5", "6")) +
     scale_color_manual(values=tcols)+
    geom_point(size=1.5) +
       xlab(" ") + ylab("Habitat Types") +
        scale_x_discrete(labels=c("Initial Habitat", "45 Hours \n Post Dispersal Habitat"))+
       scale_y_discrete(labels=c("Lowland \n Sandstone", "Alluvial \n Bench", "Freshwater \n Swamp", "Peat \n Swamp"))+
       theme(axis.text.x = element_text(family = "Georgia", size=12)) +
       theme(axis.text.y = element_text(family = "Georgia", size=12)) +
       theme(axis.title.x = element_text(family = "Georgia", size=14))+
       theme(axis.title.y = element_text(family = "Georgia", size=14))+
       labs(size ="  Number of \n Observations", color = "  Number of \n Observations", size=12)+ 
       theme(legend.title = element_text(family = "Georgia", size=12))+
       theme(legend.text = element_text(family = "Georgia", size=10))+
        guides(size = guide_legend(nrow = 3, byrow = TRUE))+
      ggtitle("A") + 
     theme(plot.title = element_text(lineheight=.8, face="bold",family = "Georgia", size=14))
plot1

#ggsave("DD45 Habitats 8Aug2020.png", plot=plot1, dpi=350, width =9, height =7)

# labs(shape = "Fruit Type", color="Predominant\n  Handling\n  Behavior") +

```

```{r}
cols_plot2<-c("#566D7E", "#307D7E", "#D4A017", "#800517", "#7D0541", "#614051")
#cols_plot2<-c("Marble Blue",  "Greenish Blue", "Orange Gold", "Firebrick", "Plum Pie", "Eggplant") 

tcols_plot2 <- makeTransparent(cols_plot2)

plot2<-ggplot(dd2_plot2, aes(x=hab_labels, y = habs, group= habitat_pairs, size=hab_pairs, color=hab_pairs)) + theme_bw()+
    geom_line() +
    scale_size_manual(values = c(1,2,4,7,8,9), labels=c("1", "2", "5", "8", "9", "10")) +
     scale_color_manual(values=tcols_plot2)+
    geom_point(size=1.5) +
    xlab(" ") + ylab("Habitat Types") +
    scale_x_discrete(labels=c("Initial Habitat", "60 Hours \n Post Dispersal Habitat"))+
   scale_y_discrete(labels=c("Lowland \n Sandstone", "Alluvial \n Bench", "Freshwater \n Swamp", "Peat \n Swamp"))+
       theme(axis.text.x = element_text(family = "Georgia", size=12)) +
       theme(axis.text.y = element_text(family = "Georgia", size=12)) +
       theme(axis.title.x = element_text(family = "Georgia", size=14))+
       theme(axis.title.y = element_text(family = "Georgia", size=14))+
       theme(legend.title = element_text(family = "Georgia", size=12))+
       theme(legend.text = element_text(family = "Georgia", size=10))+
       labs(size ="  Number of \n Observations", color = "  Number of \n Observations", size=12)+ 
       guides(size = guide_legend(nrow = 4, byrow = TRUE))+
 ggtitle("B") + 
     theme(plot.title = element_text(lineheight=.8, face="bold",family = "Georgia", size=14))
      
plot2

#ggsave("DD60 Habitats.png", plot=plot2, dpi=350, width =9, height =7)
```
```{r}

cols_plot3<-c("#307D7E", "#B38481", "#7E354D", "#D4A017", "#C35817", "#C34A2C", "#800517")
 #cols_plot3<-c("Greenish Blue", "Rosy Brown", "Velvet Maroon", "Orange Gold", "Red Fox", "Chestnut Red", "Firebrick") 
tcols_plot3 <- makeTransparent(cols_plot3)

plot3<-ggplot(dd3_plot2, aes(x=hab_labels, y = habs, group= habitat_pairs, size=hab_pairs, color=hab_pairs)) + theme_bw()+
    geom_line() +
    scale_size_manual(values = c(2,3,4,5,6,7,8), labels=c("2", "3", "4", "5", "6","7", "8"))+
    scale_color_manual(values=tcols_plot3)+
    geom_point(size=1.5) +
    xlab(" ") + ylab("Habitat Types") +
    scale_x_discrete(labels=c("Initial Habitat", "80 Hours \n Post Dispersal Habitat"))+
    scale_y_discrete(labels=c("Lowland \n Sandstone", "Alluvial \n Bench", "Freshwater \n Swamp", "Peat \n Swamp"))+
       theme(axis.text.x = element_text(family = "Georgia", size=12)) +
       theme(axis.text.y = element_text(family = "Georgia", size=12)) +
       theme(axis.title.x = element_text(family = "Georgia", size=14))+
       theme(axis.title.y = element_text(family = "Georgia", size=14)) +
       theme(legend.title = element_text(family = "Georgia", size=12))+
       theme(legend.text = element_text(family = "Georgia", size=10))+
       labs(size ="  Number of \n Observations", color = "  Number of \n Observations", size=12)+ 
      guides(size = guide_legend(nrow = 4, byrow = TRUE))+
      ggtitle("C") + 
     theme(plot.title = element_text(lineheight=.8, face="bold",family = "Georgia", size=14))
plot3

#ggsave("DD80 Habitats.png", plot=plot3, dpi=350, width =9, height =7)

```

```{r}

#all
cols_plot4<-c("#566D7E", "#307D7E")
 #cols_plot4<-c("Marble Blue",  "Greenish Blue")
tcols_plot4 <- makeTransparent(cols_plot4)

plot4<-ggplot(dd4_plot2, aes(x=hab_labels, y = habs, group= habitat_pairs, size=hab_pairs, color=hab_pairs)) + theme_bw()+
    geom_line() +
    scale_size_manual(values = c(1,2,3,4,5,6,7,8), labels=c("1", "2", "3", "4", "5", "6", "7", "8")) +
    scale_color_manual(values=tcols_plot4)+
    geom_point(size=1.5) +
    xlab(" ") + ylab("Habitat Types") +
     scale_x_discrete(labels=c("Initial Habitat", "125 Hours \n Post Dispersal Habitat"))+
    scale_y_discrete(labels=c("Lowland \n Sandstone", "Alluvial \n Bench", "Freshwater \n Swamp", "Peat \n Swamp"))+
       theme(axis.text.x = element_text(family = "Georgia", size=12)) +
       theme(axis.text.y = element_text(family = "Georgia", size=12)) +
       theme(axis.title.x = element_text(family = "Georgia", size=14))+
       theme(axis.title.y = element_text(family = "Georgia",size=14)) +
       theme(legend.title = element_text(family = "Georgia", size=12))+
       theme(legend.text = element_text(family = "Georgia", size=10))+
       labs(size ="  Number of \n Observations", color = "  Number of \n Observations", size=12)+ 
     guides(size = guide_legend(nrow = 1, byrow = TRUE))+
     ggtitle("D") + 
     theme(plot.title = element_text(lineheight=.8, face="bold",family = "Georgia", size=14))
plot4

#ggsave("DD125 Habitats.png", plot=plot4, dpi=350, width =9, height =7)


```


```{r}
plots<-grid.arrange(plot1, plot2, plot3, plot4)
plots
#ggsave("Dispersal across habitats 9Feb2021.png", plot=plots, dpi=350, width =14, height =10)

```

###----Modeling Seed Dispersal Distances Across Habitat Types in Gunung Palung National Park-----------------------
```{r}
Habitatpair<-read.csv("Orangutan_seed_dispersal_habitats.csv")
#remove all 0 occurrences
Habitatpair<-filter(Habitatpair, Number >0)
```

Modeling the effect of gut retention time, initial habitat location, and ending habitat location on the number of seed dispersal events within and across habitats. 

```{r} 
library(MASS)
#Models use a negative binomial distribution due to overdispresion (Zuur et al. 2009)
#Models use the number of occurances of dispersal events between and within each habitat as the explanatory variable.

m1_nb<-glm.nb(Number~GRT+Initial_habitat+Dispersed_habitat, data = Habitatpair)

m_intercept_nb<-glm.nb(Number~1, data = Habitatpair)

m2_nb<-glm.nb(Number~GRT,  data = Habitatpair)

m3_nb<-glm.nb(Number~GRT+Initial_habitat, data = Habitatpair)

m4_nb<-glm.nb(Number~GRT+Initial_habitat+Dispersed_habitat, data = Habitatpair)

m5_nb<-glm.nb(Number~GRT+Dispersed_habitat, data = Habitatpair)

AICtab(m_intercept_nb, m1_nb, m2_nb, m3_nb, m4_nb, m5_nb)
nb_tab<-AICtab(m_intercept_nb, m1_nb, m2_nb, m3_nb, m4_nb, m5_nb, weights=TRUE, logLik=TRUE, base=TRUE)
nb_tab<-as.data.frame(nb_tab)

#Reorder Dataframe Columns - both work
nb_tab2<-nb_tab[,c(2,4,1,3,5,6)]
nb_tab.2 <- nb_tab[, c("AIC", "dAIC", "logLik", "dLogLik", "df", "weight")]

library(rsq)
#variance explained by model
rsq(m3_nb)
```

Print out AICtab as a table 
```{r}
library(knitr)
kable(nb_tab.2, digits=2, row.names = TRUE) 
kable(nb_tab2, digits=2, row.names = TRUE) 
```

```{r}
library(data.table)

summary(m3_nb)
coef1<-as.data.frame(coef(m3_nb), make.names =TRUE)
coef2<-setDT(coef1, keep.rownames = TRUE)[]

ci1<-as.data.frame(confint(m3_nb))
ci2<-setDT(ci1, keep.rownames = TRUE)[]
ci2

ci3<-as.data.frame(confint(m3_nb, level=0.50))
ci4<-setDT(ci3, keep.rownames = TRUE)[]
ci4
m3_coef<-merge(merge(coef1, ci2, by = "rn", all = TRUE ), ci4, by = "rn", all = TRUE )

# Rename columns
names(m3_coef)[names(m3_coef) == "2.5 %"] <- "lwr95"
names(m3_coef)[names(m3_coef) == "97.5 %"] <- "upr95"
names(m3_coef)[names(m3_coef) == "25 %"] <- "lwr50"
names(m3_coef)[names(m3_coef) == "75 %"] <- "upr50"
names(m3_coef)[names(m3_coef) == "coef(m3_nb)"] <- "coef_est"

m3_coef[2, 1] <- "45 Hour GRT"
m3_coef[3, 1] <- "60 Hour GRT"
m3_coef[4, 1] <- "80 Hour GRT"
m3_coef[5, 1] <- "Initial Habitat Freshwater Swamp"
m3_coef[6, 1] <- "Initial Habitat Lowland Swamp"
m3_coef[7, 1] <- "Initial Habitat Peat Swamp"
m3_coef2<-filter(m3_coef, rn!= "(Intercept)")
m3_coef2
```
```{r}
kable(m3_coef, digits=2, row.names = FALSE) 
```
###plotting coefficients from models 
```{r}
library(forcats)

plot_c<-ggplot(data=m3_coef2, aes(x=coef_est, y=fct_rev(rn)))+geom_point()
plot_c<-plot_c+theme_classic()+labs(x="Coefficient Estimate", y=" ")
plot_c<-plot_c+geom_errorbar(aes(xmax=lwr95, xmin=upr95), width = 0.1, size  = 0.5) +
  geom_point(size  = 2.7) + geom_hline(aes(yintercept=0), size = 0.9) +
  theme(axis.title = element_text(family  = "Georgia", size=12)) + 
  geom_errorbar(aes(xmax=lwr50, xmin=upr50), width = 0.1, size  = 1) +
  theme(axis.text.x = element_text(family = "Georgia", size=12)) +
  theme(axis.text.y = element_text(family = "Georgia", size=12)) +
  theme(axis.title.x = element_text(family = "Georgia", size=12))+
  theme(axis.title.y = element_text(family = "Georgia", size=12))+
  geom_vline(xintercept=1, linetype="dashed")
plot_c

#ggsave("Dispersal Coefficients 10Feb2021.png", plot=plot_c, dpi=350, width =9, height =7)
```
Does gut retention time influence dispersal across habitats?

```{r}
m_intercept<-glm(Number~1, family = poisson(link = "log"), data = Habitatpair)

m2_GRT<-glm(Number~GRT, family = poisson(link = "log"), data = Habitatpair)
summary(m2_GRT)
exp(coef(m2_GRT))

m3_GRT<-glm(Number~GRT+Initial_habitat, family = poisson(link = "log"), data = Habitatpair)
summary(m3_GRT)
exp(coef(m3_GRT))
#reference 125-hour GRT
#reference Alluvial Initial Habitat

m4_GRT<-glm(Number~GRT+Initial_habitat+Dispersed_habitat, family = poisson(link = "log"), data = Habitatpair)
summary(m4_GRT)
exp(coef(m4_GRT))
#reference 125-hour GRT
#reference Alluvial Initial Habitat
#reference Alluvial Dispersed Habitat
exp(confint(m4_GRT))
exp(confint(m4_GRT, full = T, level=0.5))

(coef(m4_GRT))
(confint(m4_GRT))
c<-(confint(m4_GRT, level=0.5))
write.csv(c, "confint_50.csv")

m5_GRT<-glm(Number~GRT+Dispersed_habitat, family = poisson(link = "log"), data = Habitatpair)
summary(m5_GRT)
exp(coef(m5_GRT))

AICtab(m_intercept,m2_GRT, m3_GRT,m4_GRT,m5_GRT, weights = TRUE, logLik=TRUE, base=TRUE)
#model 4, best model (df=10, weight=0.86)
```






