---
title: "Modeling Instraspecific Variation in Orangutan Seed Dispersal Distances in Gunung Palung National Park, Indonesia"
author: "Andrea Blackburn"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(DHARMa)
library(glmmTMB)
library(dplyr)
library(tidyr)
library(lme4)
library(lubridate)
library(bbmle)
library(MASS)
library(rsq)
library(optimx)
library(knitr)
library(lmerTest)
library(data.table)
```


```{r}
#read in seed dispersal distances
#dataset contains phenology data (column zscore_MR)
dd<-read.csv("Bornean_orangutan_seed_dispersal_distances_dataset.csv")
dd<-tbl_df(dd)
```

```{r}
#split dataset by Dispersal distance transit time and remove NA's

#45 hour transit time seed dispersal distances 
dd1<-filter(dd, DD.45 != "0")
#60 hour transit time seed dispersal distances 
dd2<-filter(dd, DD.60 != "0")
#80 hour transit time seed dispersal distances 
dd3<-filter(dd, DD.80 != "0")
#125 hour transit time seed dispersal distances 
dd4<-filter(dd, DD.125 != "0")
```

##Modeling Dispersal Distances by Gut Passage Duration
The effect of gut passage time on modeled seed dispersal distances of Bornean orangutans 

```{r}
#recombine dispersal distances from across all four gut rention times
disp_dist<-c(dd1$DD.45, dd2$DD.60, dd3$DD.80, dd4$DD.125)
GRT<-c(rep("GRT45", length(dd1$DD.45)), rep("GRT60", length(dd2$DD.60)), rep("GRT80", length(dd3$DD.80)), rep("GRT125", length(dd4$DD.125)))
dispersal<-data.frame(disp_dist, GRT)

#Intercept (Null) Model
#Model distribution: gamma, link function: log
dd_m1<-glm(disp_dist~1, family = Gamma(link = "log"), data = dispersal)
coef(dd_m1)
summary(dd_m1)
#Model with gut retention time(GRT) as a predictor
dd_m2<-glm(disp_dist~GRT, family = Gamma(link = "log"), data = dispersal)
summary(dd_m2)
coef(dd_m2)
exp(coef(dd_m2))
exp(confint(dd_m2))
confint(dd_m2)

#AIC comparison
AICtab(dd_m1, dd_m2, weights=TRUE, logLik=TRUE, base=TRUE)
```
##45 Hour Gut rention time (GRT) and & Seed Dispersal Distances
````{r}
#change to factors
dd1$Orangutan<-as.factor(dd1$Orangutan)
dd1$Age.sex<-as.factor(dd1$Age.sex)
#If lost the the orangutan before 4 full days = 1, otherwise fill in with 0's
dd1$lost<-as.factor(ifelse(dd1$Lost_unable_to_follow == "Y", 1 , 0))


#intercept model:
M45_1 = glmer(DD.45~1 +(1|Orangutan), family = Gamma(link = "log"), 
          data = dd1,  
          control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
M45.1<-c("~1")
summary(M45_1)

#Models with predictor variables phenology (zscore_MR), orangutan age-sex class (Age.sex), and if the orangutan was lost during the follow series (lost)
M45_2<-glmer(DD.45 ~ zscore_MR+ (1|Orangutan), family = Gamma(link = "log"), 
          data = dd1,
          control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))

M45.2<-c("~phenology")

M45_3<-glmer(DD.45 ~ lost + (1|Orangutan), family = Gamma(link = "log"), 
           data = dd1,
          control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
summary(M45_3)
M45.3<-c("~lost")

M45_4<-glmer(DD.45 ~ Age.sex + (1|Orangutan), family = Gamma(link = "log"), 
             data = dd1,
              control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
M45.4<-c("~age-sex")

M45_5<-glmer(DD.45 ~ zscore_MR + lost+Age.sex + (1|Orangutan), family = Gamma(link = "log"), 
             data = dd1,
             control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
M45.5<-c("~phenology + lost + age-sex")

M45_6<-glmer(DD.45 ~ Age.sex + lost + (1|Orangutan), family = Gamma(link = "log"), 
             data = dd1,
              control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
M45.6<-c("~age-sex + lost")

M45_7<-glmer(DD.45 ~ Age.sex + zscore_MR + (1|Orangutan), family = Gamma(link = "log"), 
           data = dd1,
           control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
M45.7<-c("~phenology + age-sex")

M45_8<-glmer(DD.45 ~ lost + zscore_MR + (1|Orangutan), family = Gamma(link = "log"),
           data = dd1,
           control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
M45.8<-c("~phenology + lost")
summary(M45_8)

AICtab(M45_1, M45_2, M45_3, M45_4, M45_5, M45_6, M45_7, M45_8, weights=TRUE, logLik=TRUE, base=TRUE)
tab_45aic<-AICtab(M45_1, M45_2, M45_3, M45_4, M45_5, M45_6, M45_7, M45_8, weights=TRUE, logLik=TRUE, base=TRUE)
names45<-c(M45.1, M45.2, M45.3, M45.4, M45.5, M45.6, M45.7, M45.8)
rn<-c("M45_1", "M45_2", "M45_3", "M45_4", "M45_5", "M45_6", "M45_7","M45_8")

table_45<-data.frame(rn, names45)
tab_45aic<-as.data.frame(tab_45aic)
#make row names into columns
tab_45aic<-setDT(tab_45aic, keep.rownames = TRUE)[]
table2_45<-merge(tab_45aic, table_45, by="rn")
#sort by AIC
table2_45 <- table2_45[order(AIC),]


#How much variance is explained by each model?
rsq(M45_3)
rsq(M45_1)
rsq(M45_8)
```
Create a table comparing model outputs
```{r}
knitr::kable(table2_45, digits=2, row.names = FALSE) 
```
##60 Hour GRT & Dispesal Distances
````{r}
#change to factors
dd2$Orangutan<-as.factor(dd2$Orangutan)
dd2$Age.sex<-as.factor(dd2$Age.sex)
#If lost the the orangutan before 4 full days = 1, otherwise fill in with 0's
dd2$lost<-as.factor(ifelse(dd2$Lost_unable_to_follow == "Y", 1 , 0))

#intercept model:
M60_1 = glmer(DD.60~1 +(1|Orangutan), family = Gamma(link = "log"), 
              data = dd2,  
              control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
M60.1<-c("~1")

#Models with predictor variables phenology (zscore_MR), orangutan age-sex class (Age.sex), and if the orangutan was lost during the follow series (lost)
M60_2<-glmer(DD.60 ~ zscore_MR+ (1|Orangutan), family = Gamma(link = "log"), 
             data = dd2,
             control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
M60.2<-c("~phenology")

M60_3<-glmer(DD.60 ~ lost + (1|Orangutan), family = Gamma(link = "log"), 
             data = dd2,
             control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
summary(M60_3)
M60.3<-c("~lost")

M60_4<-glmer(DD.60 ~ Age.sex + (1|Orangutan), family = Gamma(link = "log"), 
             data = dd2,
             control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
M60.4<-c("~age-sex")

M60_5<-glmer(DD.60 ~ zscore_MR + lost+Age.sex + (1|Orangutan), family = Gamma(link = "log"), 
            data = dd2,
            control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
M60.5<-c("~phenology + lost + age-sex")

M60_6<-glmer(DD.60 ~ Age.sex + lost + (1|Orangutan), family = Gamma(link = "log"), 
             data = dd2,
             control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
M60.6<-c("~age-sex + lost")
summary(M60_6)

M60_7<-glmer(DD.60 ~ Age.sex + zscore_MR + (1|Orangutan), family = Gamma(link = "log"), 
             data = dd2,
            control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
M60.7<-c("~phenology + age-sex")

M60_8<-glmer(DD.60 ~ lost + zscore_MR + (1|Orangutan), family = Gamma(link = "log"),
             data = dd2,
             control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
M60.8<-c("~phenology + lost")
summary(M60_8)

AICtab(M60_1, M60_2, M60_3, M60_4, M60_5, M60_6, M60_7, M60_8, weights=TRUE, logLik=TRUE, base=TRUE)
tab_60aic<-AICtab(M60_1, M60_2, M60_3, M60_4, M60_5, M60_6, M60_7, M60_8, weights=TRUE, logLik=TRUE, base=TRUE)
names60<-c(M60.1, M60.2, M60.3, M60.4, M60.5, M60.6, M60.7, M60.8)
rn<-c("M60_1", "M60_2", "M60_3", "M60_4", "M60_5", "M60_6", "M60_7","M60_8")
table_60<-data.frame(rn, names60)

tab_60aic<-as.data.frame(tab_60aic)
#make row names into columns
tab_60aic<-setDT(tab_60aic, keep.rownames = TRUE)[]
table2_60<-merge(tab_60aic, table_60, by="rn")
#sort by AIC
table2_60 <- table2_60[order(AIC),]

#How much variance is explained by each top model
rsq(M60_3)
rsq(M60_8)
```
Create a table comparing model outputs
```{r}
kable(table2_60, digits=2, row.names = FALSE) 
```
##80 Hour GRT & Seed Dispersal Distances
````{r}
dd3$Orangutan<-as.factor(dd3$Orangutan)
dd3$Age.sex<-as.factor(dd3$Age.sex)

#intercept model:
M80_1 = glmer(DD.80~1 +(1|Orangutan), family = Gamma(link = "log"), 
              data = dd3,  
              control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
M80.1<-c("~1")
summary(M80_1)

#Models with predictor variables phenology (zscore_MR) and orangutan age-sex class (Age.sex)
M80_2<-glmer(DD.80 ~ zscore_MR+ (1|Orangutan), family = Gamma(link = "log"), 
             data = dd3,
             control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))

M80.2<-c("~phenology")
summary(M80_2)

M80_3<-glmer(DD.80 ~ Age.sex + (1|Orangutan), family = Gamma(link = "log"), 
             data = dd3,
            control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
M80.3<-c("~age-sex")
summary(M80_3)

M80_4<-glmer(DD.80 ~ Age.sex + zscore_MR + (1|Orangutan), family = Gamma(link = "log"), 
             data = dd3,
             control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
M80.4<-c("~phenology + age-sex")

AICtab(M80_1, M80_2, M80_3, M80_4, weights=TRUE, logLik=TRUE, base=TRUE)
tab_80aic<-AICtab(M80_1, M80_2, M80_3, M80_4, weights=TRUE, logLik=TRUE, base=TRUE)
names80<-c(M80.1, M80.2, M80.3, M80.4)
rn<-c("M80_1", "M80_2", "M80_3", "M80_4")
table_80<-data.frame(rn, names80)

tab_80aic<-as.data.frame(tab_80aic)
#make row names into columns
tab_80aic<-setDT(tab_80aic, keep.rownames = TRUE)[]
table2_80<-merge(tab_80aic, table_80, by="rn")
#sort by AIC
table2_80 <- table2_80[order(AIC),]

#How much variance is explained by each top model
rsq(M80_1)
rsq(M80_2)
```
Create a table comparing model outputs
```{r}
knitr::kable(table2_80, digits=2, row.names = FALSE) 
```

##125 hour GRT & seed dispersal distances
````{r}
dd4$Orangutan<-as.factor(dd4$Orangutan)
dd4$Age.sex<-as.factor(dd4$Age.sex)

#intercept model:
M125_1 = glmer(DD.125~1 +(1|Orangutan), family = Gamma(link = "log"), 
              data = dd4,  
              control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
M125.1<-c("~1")
summary(M125_1)

#Models with predictor variables phenology (zscore_MR) and orangutan age-sex class (Age.sex)
M125_2<-glmer(DD.125 ~ zscore_MR+ (1|Orangutan), family = Gamma(link = "log"), 
            data = dd4,
           control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
summary(M125_2)
M125.2<-c("~phenology")

M125_3<-glmer(DD.125 ~ Age.sex + (1|Orangutan), family = Gamma(link = "log"), 
             data = dd4,
            control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
M125.3<-c("~age-sex")
summary(M125_3)

M125_4<-glmer(DD.125 ~ Age.sex + zscore_MR + (1|Orangutan), family = Gamma(link = "log"), 
            data = dd4,
            control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
M125.4<-c("~phenology + age-sex")
summary(M125_4)

AICtab(M125_1, M125_2, M125_3, M125_4, weights=TRUE, logLik=TRUE, base=TRUE)

tab_125aic<-AICtab(M125_1, M125_2, M125_3, M125_4, weights=TRUE, logLik=TRUE, base=TRUE)

names125<-c(M125.1, M125.2, M125.3, M125.4)
rn<-c("M125_1", "M125_2", "M125_3", "M125_4")
table_125<-data.frame(rn, names125)

tab_125aic<-as.data.frame(tab_125aic)
#make row names into columns
tab_125aic<-setDT(tab_125aic, keep.rownames = TRUE)[]
table2_125<-merge(tab_125aic, table_125, by="rn")
#sort by AIC
table2_125 <- table2_125[order(AIC),]

#How much variance is explained by each top model
rsq(M125_2)
rsq(M125_4)

```
Create a table comparing model outputs
```{r}
knitr::kable(table2_125, digits=2, row.names = FALSE) 
```

```{r}
#By what percent does mean dispersal distance increase in lost & unable to follow series versus non-lost follow series?

#45-hours
((622-431)/431)*100
#44.31%
#for 45-hour seeds dispersal distances during lost  & unable to follow series were 44.3% longer than during not-lost follow series

#60-hours
((845-491)/491)*100
#72.09%
#for 60-hour seed dispersal distances during lost  & unable to follow series were 72.1% longer than during not-lost follow series
```

